Automated Topic Naming

### 2012-01-20 ese/ese-major-response.tex
formatting response

We would like to thank you for your thorough reviews. We addressed all
5 major revision points and we then we tried to address all of the
smaller reviewer comments, edits. We have a giant TODO file that was
compiled from the very thorough four reviews our paper received, and
we achieved, met, and integrated all of those comments, edits, and
requirements into this revision of the paper.

\begin{quotation}
 The reviewers would like to see discussion of the relationship of
 the current draft and the previous MSR 2011 paper and more detailed
 discussion of previous papers related to the current draft. 
\end{quotation}

@@

\begin{quotation}
     The reviewers have several requests for more details of the study
   design choices (e.g., choosing projects from the same application
   domain, using ROC instead of F-Measure as your primary measure) and
   some related discussion on the threats to validity.
\end{quotation}

@@

\begin{quotation}
  Fix writing: The reviewers point out quite some inconsistent and
  unclear writing in various places of the paper.
\end{quotation}

@@

\begin{quotation}
 Reviewer 3 raises that the extremely low IRR (~0.1) threatens the
   validity of the results of these experiments, and its threats to
   validity should be made more prominent.

\end{quotation}

@@

\begin{quotation}
 Reviewer 4 raises the some observed results may simply be due to
 the differences among developer styles and not necessarily
 reflecting different types of work.  
\end{quotation}

>>>>

We would like to thank you for your thorough reviews. In our revised paper,
we have addressed all five  major revision points. In addition, we incorporated nearly all of the
minor reviewer comments and corrections. 
% one exception: the timeline figure is still fairly small.
%We have a giant TODO file that was 
% compiled from the very thorough four reviews our paper received, and
% we achieved, met, and integrated all of those comments, edits, and
% requirements into this revision of the paper.

We now explain how we have amended the paper to incorporate the major revisions requested.

\subsubsection*{1. The reviewers would like to see discussion of the relationship of
 the current draft and the previous MSR 2011 paper and more detailed
 discussion of previous papers related to the current draft.}

@@

\subsubsection*{2. The reviewers have several requests for more details of the study
   design choices (e.g., choosing projects from the same application
   domain, using ROC instead of F-Measure as your primary measure) and
   some related discussion on the threats to validity.}

@@

\subsubsection*{
  3. Fix writing: The reviewers point out quite some inconsistent and
  unclear writing in various places of the paper.}

@@

\subsubsection*{4.  Reviewer 3 raises that the extremely low IRR (~0.1) threatens the
   validity of the results of these experiments, and its threats to
   validity should be made more prominent.}

@@

\subsubsection*{5. Reviewer 4 raises the some observed results may simply be due to
 the differences among developer styles and not necessarily
 reflecting different types of work. }

### 2012-01-20 ese/ese.tex
formatting response

\section{Understanding Software Maintenance Activities} 
\label{sec:analysis}
%XXX Neil should we remove this cite?
As we mentioned in the introduction, a key issue in software
maintenance is understanding \emph{why} a system has evolved the way
it has: Aranda et al.~\cite{aranda09icse} explored \emph{why}, in
terms of how a bug actually occurred and was documented.
In this section we demonstrate the value of labelled topic extraction
in addressing this issue. 
% more why
Labelled topics address \emph{why} questions by associating a commit with the underlying software qualities which motivated that change.
The \emph{how} of a change is the change itself, the software quality behind it, the
\emph{why} is what we are after.
We investigate the history of the three large-scale database systems that we studied. 
We use our technique to show the topic of development efforts over time in each project.
%We evaluated two research questions using the ground truth data that we annotated by hand:
We motivated our investigation with three research questions:
\renewcommand{\labelenumi}{\textbf{RQ\arabic{enumi}. }}
\begin{enumerate}
\item \emph{Do NFR frequencies change over time?} If a particular NFR
  was of more interest at one point in the life-cycle than another,
  this suggests that development activity shifted focus. For example,
  if a developer expected to see a recent focus on \emph{reliability},
  but instead \emph{usability} dominated, they might re-prioritize
  upcoming work items.

>>>>

\section{Understanding Software Maintenance Activities} 
\label{sec:analysis}
%XXX Neil should we remove this cite?
As we mentioned in the introduction, a key issue in software
maintenance is understanding \emph{why} a system has evolved the way
it has. 
% Aranda et al.~\cite{aranda09icse} explored \emph{why}, in
%terms of how a bug actually occurred and was documented.
In this section we demonstrate the value of labelled topic extraction
in addressing this issue. 
% more why
Labelled topics address \emph{why} questions by associating a commit with the underlying software qualities which motivated that change.
The \emph{how} of a change is the change itself, the software quality behind it, the
\emph{why} is what we are after.
We investigate the history of the three large-scale database systems that we studied. 
We use our technique to show the topic of development efforts over time in each project.
%We evaluated two research questions using the ground truth data that we annotated by hand:
We motivated our investigation with three research questions:
\renewcommand{\labelenumi}{\textbf{RQ\arabic{enumi}. }}
\begin{enumerate}
\item \emph{Do NFR frequencies change over time?} If a particular NFR
  was of more interest at one point in the life-cycle than another,
  this suggests that development activity shifted focus. For example,
  if a developer expected to see a recent focus on \emph{reliability},
  but instead \emph{usability} dominated, they might re-prioritize
  upcoming work items.
